### 2023-05-26 definitions.tex
sections

{\bf On effectivity}
A WSTS $\mathscr{S}=(S, \rightarrow, \leq)$ is {\em effective} if there exists a pair of algorithms
($M_\rightarrow$, $M_\leq$) operating on $\N \times \N$ such that
$ M_\rightarrow$ computes the transition relation “$\rightarrow$” and 
$M_\leq$ the ordering relation “$\leq$”.

A WSTS $\mathscr{S}=(S, \rightarrow, \leq)$ has {\em effective pred-basis} \cite{DBLP:journals/tcs/FinkelS01,DBLP:journals/iandc/AbdullaCJT00} if there exists an algorithm accepting
any state $s \in S$ and returning $pb(s)$, a finite basis of $\uparrow \pred(\uparrow s)$.

@@

%We say that $\mathscr{S}$ is {\em upward pre-effective} if it is effective,
%and if there exists an additional Turing machine that computes a finite basis of 
%$\uparrow \pred (\uparrow x)$
%on input $x$, where $x$ is a state of $\mathscr{S}$.

We say that $\mathscr{S}$
is {\em ideally effective} \cite{BFM-ic17} if (1) the function mapping the encoding of a configuration $s$
to the encoding of the ideal $\downarrow s$ is computable; (2) inclusion of ideals is decidable; (3) the downward closure $\downarrow \post(I)$ expressed as a finite union of ideals is computable from the ideal $I$.
%
\iffalse
%%%%%%%%%

>>>>

{\bf On effectivity}
Let a WSTS $\mathscr{S}=(S, \rightarrow, \leq)$. We say that $\mathscr{S}$ is {\em effective} if there exists a pair of algorithms
($M_\rightarrow$, $M_\leq$) operating on $\N \times \N$ such that
$ M_\rightarrow$ computes the transition relation “$\rightarrow$” and 
$M_\leq$ the ordering relation “$\leq$”.

We say that $\mathscr{S}=(S, \rightarrow, \leq)$ has {\em effective pred-basis} \cite{DBLP:journals/tcs/FinkelS01,DBLP:journals/iandc/AbdullaCJT00} if there exists an algorithm accepting
any state $s \in S$ and returning $pb(s)$, a finite basis of $\uparrow \pred(\uparrow s)$.

We say that $\mathscr{S}$
is {\em ideally effective} \cite{BFM-ic17} if (1) the function mapping the encoding of a configuration $s$
to the encoding of the ideal $\downarrow s$ is computable; (2) inclusion of ideals is decidable; (3) the downward closure $\downarrow \post(I)$ expressed as a finite union of ideals is computable from the ideal $I$.

@@

%We say that $\mathscr{S}$ is {\em upward pre-effective} if it is effective,
%and if there exists an additional Turing machine that computes a finite basis of 
%$\uparrow \pred (\uparrow x)$
%on input $x$, where $x$ is a state of $\mathscr{S}$. 
%
\iffalse
%%%%%%%%%
